Output Summary

### 2023-05-04 03-post-process/output-plots-children/12-param-summaries.Rmd
Consistency updates: 06-length-based-survival.Rmd

```{r my-boxplot-function}
my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = alpha("salmon", 0.5), border = alpha("red", 0.5), las = 3, ...) {
  # extract posterior samples and rename them
  post_sub = post_subset(post, params, matrix = TRUE)

@@

  # replace the summary stats with my preferred quantiles
  par(mar = c(5,3,1,1), mgp = c(2,0.35,0), tcl = -0.15)
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, las = las, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)
} 
```

## Egg-to-Parr Survival {.tabset .tabset-pills}

### Beverton-Holt Parameters

```{r egg-to-parr-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("^alpha[.]", "Productivity")
my_boxplot("^beta[.]", "Capacity")
```

@@

```{r egg-to-parr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("^sig_Lphi_E_Pb[.]", "Process SD", ylim = c(0,2))
my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); abline(h = 0, lty = 2)
my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklabs = vcov_labels); abline(h = 0, lty = 2)
```

## Summer Parr Size

```{r summer-size-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^omega0[.]$", "Intercept")
my_boxplot("^omega1[.]$", "Slope"); abline(h = 0, lty = 2)
my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Life History Apportionment

```{r LH-type-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Mean Proportion Fall Migrants", ylim = c(0,1))
my_boxplot("sig_Lpi[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("^rho_Lpi", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

@@

### Logistic Function Parameters

```{r overwinter-survival-bxp1, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept (Fall)")
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept (Spring)")
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope (Fall)"); abline(h = 0, lty = 2)
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_spring, pop = "."), "Slope (Spring)"); abline(h = 0, lty = 2)
```

@@

```{r overwinter-survival-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lphi_Pa_Mb[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels); abline(h = 0, lty = 2)
```

## "Growth" Factor

```{r growth-factor-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^theta0[.]$", "Intercept")
my_boxplot("^theta1[.]$", "Slope"); abline(h = 0, lty = 2)
my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Movement Survival to LGR {.tabset .tabset-pills}

### Mean/Logistic Model Parameters

```{r trib-to-lgr-bxp1, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("tau0", "Intercept", main = "NOR")
my_boxplot("tau1", "Slope", main = "NOR"); abline(h = 0, lty = 2)
my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = "."), "Average Migration Survival", main = "HOR", ylim = c(0,1))
```

@@

```{r trib-to-lgr-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Movement Survival to Ocean

```{r lgr-to-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Ma_O0", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Ma_O0[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
```

## Probability of Maturing at Age-3 {.tabset .tabset-pills}

@@

```{r age3-mean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
```

@@

```{r age3-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## Probability of Maturing at Age-4 {.tabset .tabset-pills}

@@

```{r age4-mean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "", main = "NOR", ylim = c(0,1))
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = "."), "", main = "HOR", ylim = c(0,1))
```

@@

```{r age4-sd-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot("sig_Lpsi_O2[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Among-pop Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

@@

```{r yr1-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

@@

```{r yr1-ocean-bxp2, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); abline(h = 0, lty = 2)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Among-pop Correlation", ylim = c(-1,1)); abline(h = 0, lty = 2)
```

@@

```{r yr2-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

@@

```{r yr3-ocean-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,2))
my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), main = "NOR", ylim = c(0,1), ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), main = "HOR", ticklabs = pops[c(1,2,4)], ylim = c(0,1), ylab = "Average Survival")
```

@@

```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5}

# par(mfrow = c(1,3))
tmp_ylim = c(-1.5,1.5)
my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 1", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
# my_boxplot(sub_index("delta_O1_O2[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 2", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
# my_boxplot(sub_index("delta_O2_O3[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", main = "Year 3", ticklabs = pops[c(1,2,4)], ylim = tmp_ylim); abline(h = 0, lty = 2)
```

## Movement Survival BON to LGR

```{r bon-to-lgr-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Rb_Ra", "Average Migration Survival", ylim = c(0,1), ticklab = origins)
my_boxplot("sig_Lphi_Rb_Ra[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Among-origin Correlation", ylim = c(-1,1), ticklab = c("")); abline(h = 0, lty = 2)
```

@@

```{r prespawn-surv-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,3))
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = c(0,1))
my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Among-pop Correlation", ylim = c(-1,1), ticklab = vcov_labels); abline(h = 0, lty = 2)
```

>>>>

```{r my-boxplot-function}
my_boxplot = function(params, ylab = NULL, ticklabs = pops, ylim = NULL, boxfill = tran_cols["model"], border = main_cols["model"], las = 3, label_text = NULL, ...) {
  # extract posterior samples and rename them
  post_sub = post_subset(post, params, matrix = TRUE)

@@

  # replace the summary stats with my preferred quantiles
  bp$stats = apply(post_sub, 2, function(x) quantile(x, c(0.025, 0.25, 0.5, 0.75, 0.975)))
  if (is.null(ylim)) ylim = make_lim(bp$stats)
  bxp(bp, ylab = ylab, xlab = "", outline = FALSE, ylim = ylim, las = las, ...,
      staplelty = 0, whisklty = 1, boxfill = boxfill, boxcol = border, medcol = border, whiskcol = border)

  axis_labels(ylab = ylab, outer = FALSE, yline = 1)
  panel_label(label_text, "topleft")
}

ref_line = function(h) {
  abline(h = h, col = par("col.axis"), lty = 2)
}

bp_mar = c(3,2,1,1)
bp_oma = c(0.2,0.2,0,0)
```

## Egg $\to$ Parr Survival {.tabset .tabset-pills}

### Coefficients (BH Parameters)

```{r egg-to-parr-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^alpha[.]", "Productivity")
my_boxplot("^beta[.]", "Capacity")
```

@@

```{r egg-to-parr-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_Lphi_E_Pb[.]", "Process SD", ylim = c(0,2))
my_boxplot("^kappa_phi_E_Pb[.]", "AR(1) Coef.", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("^rho_Lphi_E_Pb", vcov_inds), "Correlation", ylim = c(-1,1), ticklabs = vcov_labels); ref_line(h = 0)
```

## Parr Mean Length {.tabset .tabset-pills}

### Coefficients

```{r summer-size-bxp1, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^omega0[.]$", "Intercept")
my_boxplot("^omega1[.]$", "Slope"); ref_line(h = 0)
```

```{r summer-size-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_lL_Pb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lL_Pb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Migratory Strategy Apportionment

```{r LH-type-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_pi[LH_type,pop]", LH_type = i_fall, pop = "."), ylab = "Average Pr(Fall)", ylim = ylim_01)
my_boxplot("sig_Lpi[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("^rho_Lpi", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

@@

### Coefficients

```{r overwinter-survival-bxp1, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_fall, pop = "."), "Intercept", label_text = "Fall Migrants")
my_boxplot(sub_index("gamma0[LH_type,pop]", LH_type = i_spring, pop = "."), "Intercept", label_text = "Spring Migrants")
my_boxplot(sub_index("gamma1[LH_type,pop]", LH_type = i_fall, pop = "."), "Slope", label_text = "Fall & Spring Migrants"); ref_line(h = 0)
```

@@

```{r overwinter-survival-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_Pa_Mb[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Pa_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels); ref_line(h = 0)
```

## Parr $\to$ Smolt "Growth" Factor {.tabset .tabset-pills}

### Coefficients

```{r growth-factor-bxp1, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^theta0[.]$", "Intercept")
my_boxplot("^theta1[.]$", "Slope"); ref_line(h = 0)
```

@@

```{r growth-factor-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("^sig_lDelta_L_Pb_Mb[.]$", "Process SD", ylim = c(0,0.5))
my_boxplot(paste0("^rho_lDelta_L_Pb_Mb", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Smolt $\to$ LGR Survival {.tabset .tabset-pills}

### Coefficients

```{r trib-to-lgr-bxp1, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("tau0", "Intercept", label_text = "NOR")
my_boxplot("tau1", "Slope", label_text = "NOR"); ref_line(h = 0)
my_boxplot(sub_index("mu_phi_Mb_Ma[LH_type,origin,pop]", LH_type = i_spring, origin = o_hor, pop = c(1,2,4)), "Average Survival", label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01)
```

```{r trib-to-lgr-bxp2, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_Mb_Ma[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Mb_Ma", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); abline(h = 0, lty = 2)
```

## LGR $\to$ BON Survival

```{r lgr-to-ocean-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Ma_O0", "Average Survival", ylim = ylim_01, ticklab = origins)
my_boxplot("sig_Lphi_Ma_O0[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Ma_O0[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
```

## Pr(Mature Age-3) {.tabset .tabset-pills}

@@

```{r age3-mean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-3)", label_text = "NOR", ylim = ylim_01)
my_boxplot(sub_index("mu_psi_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-3)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
```

@@

```{r age3-sd-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lpsi_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O1", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

## Pr(Mature Age-4) {.tabset .tabset-pills}

@@

```{r age4-mean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_nor, pop = "."), "Pr(Mature Age-4)", label_text = "NOR", ylim = ylim_01)
my_boxplot(sub_index("mu_psi_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), "Pr(Mature Age-4)", label_text = "HOR", ylim = ylim_01, ticklabs = pops[c(1,2,4)])
```

@@

```{r age4-sd-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lpsi_O2[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lpsi_O2", vcov_inds), "Correlation", ticklabs = vcov_labels, ylim = c(-1,1)); ref_line(h = 0)
```

@@

```{r yr1-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O0_O1[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O0_O1[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

@@

```{r yr1-ocean-bxp2, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("sig_Lphi_O0_O1[", ylab = "Process SD", ylim = c(0,2))
my_boxplot(sub_index("kappa_phi_O0_O1[pop]", pop = "."), ylab = "Autocorrelation", ylim = c(-1,1)); ref_line(h = 0)
my_boxplot(paste0("rho_Lphi_O0_O1", vcov_inds), ticklabs = vcov_labels, ylab = "Correlation", ylim = c(-1,1)); ref_line(h = 0)
```

@@

```{r yr2-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O1_O2[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O1_O2[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

@@

```{r yr3-ocean-bxp, fig.width = p2_width, fig.height = p2_height}
mypar(mfrow = c(1,2), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("mu_phi_O2_O3[origin,.]", origin = o_nor), label_text = "NOR", ylim = ylim_01, ylab = "Average Survival")
my_boxplot(sub_index("mu_phi_O2_O3[origin,pop]", origin = o_hor, pop = c(1,2,4)), label_text = "HOR", ticklabs = pops[c(1,2,4)], ylim = ylim_01, ylab = "Average Survival")
```

@@

```{r ocean-surv-scaler, fig.width = 4, fig.height = 3.5, out.width = "50%"}
mypar(mfrow = c(1,1), mar = bp_mar, oma = bp_oma)
my_boxplot(sub_index("delta_O0_O1[pop]", pop = c(1,2,4)), ylab = "Log Odds Ratio", ticklabs = pops[c(1,2,4)], ylim = c(-1.5,1.5)); ref_line(h = 0)
```

## BON $\to$ LGR Survival

```{r bon-to-lgr-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Rb_Ra", "Average Survival", ylim = ylim_01, ticklab = origins)
my_boxplot("sig_Lphi_Rb_Ra[", "Process SD", ticklab = origins, ylim = c(0,2))
my_boxplot("rho_Lphi_Rb_Ra[2,1]", "Correlation (Origins)", ylim = c(-1,1), ticklab = c("")); ref_line(h = 0)
```

@@

```{r prespawn-surv-bxp, fig.width = p3_width, fig.height = p3_height}
mypar(mfrow = c(1,3), mar = bp_mar, oma = bp_oma)
my_boxplot("mu_phi_Sb_Sa", "Average Survival", ylim = ylim_01)
my_boxplot("sig_Lphi_Sb_Sa[", "Process SD", ylim = c(0,2))
my_boxplot(paste0("rho_Lphi_Sb_Sa", vcov_inds), "Correlation", ylim = c(-1,1), ticklab = vcov_labels); ref_line(h = 0)
```

### 2023-05-04 03-post-process/output-plots-children/13-post-vs-prior.Rmd
Consistency updates: 06-length-based-survival.Rmd

```{r post-v-prior-fn}
post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, n_bins = 50, alpha = 0.5) {

@@

  # graphics parameters
  par(xaxs = "i", yaxs = "i", mgp = c(2,0.2,0), cex.axis = 0.8, tcl = -0.15, mar = c(1.5,1,1.5,0.5), lend = "square", ljoin = "mitre")

@@

@@

  # draw segments to connect axes at origin
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE)
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE)

@@

  # function to plot one population/pair
  plot_f = function(j) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
      main = titles[j], 
      legend_loc = ifelse(j == looping[1], legend_loc, NA),
      y_max = y_max,
      xlim = xlim
    )
  }

  # apply to each population/pair
  par(mfrow = mfrow, oma = c(1,1.75,0,0))
  junk = sapply(1:n, function(j) plot_f(looping[j]))
  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
}

# wrapper to create plot for all origins
post_v_prior_origins = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, ...) {
  # function to plot one population
  plot_f = function(o) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, origin = o, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, origin = o, ...), matrix = TRUE),
      main = c("NOR", "HOR")[o], 
      legend_loc = ifelse(o == 1, legend_loc, NA),
      xlim = xlim
    )
  }

  # apply to each origin
  par(mfrow = c(1,2), oma = c(1,1.5,0,0))
  junk = sapply(1:jags_data$no, plot_f)
  mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
  mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
}
```

@@

```{r rho_Lphi_Ma_O0-post-v-prior, fig.width = 3, fig.height = 3}
par(oma = c(1,1.75,0,0))
post_v_prior(post_samps = post_subset(post, "rho_Lphi_Ma_O0[2,1]", matrix = TRUE),
             prior_samps = post_subset(post, "rho_Lphi_Ma_O0_pr[2,1]", matrix = TRUE),
             xlim = xlim, y_max = y_max)
mtext(side = 1, outer = TRUE, line = 0, "Parameter Value")
mtext(side = 2, outer = TRUE, line = 0.5, "Probability")
```

>>>>

```{r post-v-prior-fn}
post_v_prior = function(post_samps, prior_samps, prior_col = "salmon", post_col = "royalblue",
                        main = NULL, y_max = 0.5, xlim = NULL, legend_loc = NA, label_text = NULL, n_bins = 50, alpha = 0.5) {

@@

  # graphics parameters
  par(xaxs = "i", yaxs = "i")

@@

  panel_label(label_text)

@@

  # draw segments to connect axes at origin
  usr = par("usr"); xdiff = diff(usr[1:2]); ydiff = diff(usr[3:4])
  segments(usr[1], usr[3], usr[2], usr[3], xpd = TRUE, col = par("col.axis"))
  segments(usr[1], usr[3], usr[1], usr[4], xpd = TRUE, col = par("col.axis"))

@@

  # function to plot one population/pair
  plot_f = function(j) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, pop = j, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, pop = j, ...), matrix = TRUE),
      label_text = titles[j], 
      legend_loc = ifelse(j == looping[1], legend_loc, NA),
      y_max = y_max,
      xlim = xlim
    )
  }

  # apply to each population/pair
  mypar(mfrow = mfrow)
  junk = sapply(1:n, function(j) plot_f(looping[j]))
  axis_labels("Parameter Value", "Probability")
}

# wrapper to create plot for all origins
post_v_prior_origins = function(post_param, prior_param, legend_loc = "topright", xlim = NULL, ...) {
  # function to plot one population
  plot_f = function(o) {
    post_v_prior(
      post_samps = post_subset(post, sub_index(post_param, origin = o, ...), matrix = TRUE),
      prior_samps = post_subset(post, sub_index(prior_param, origin = o, ...), matrix = TRUE),
      label_text = c("NOR", "HOR")[o], 
      legend_loc = ifelse(o == 1, legend_loc, NA),
      xlim = xlim
    )
  }

  # apply to each origin
  mypar(mfrow = c(1,2))
  junk = sapply(1:jags_data$no, plot_f)
  axis_labels("Parameter Value", "Probability")
}
```

@@

```{r rho_Lphi_Ma_O0-post-v-prior, fig.width = 3, fig.height = 3}
mypar(mfrow = c(1,1))
post_v_prior(post_samps = post_subset(post, "rho_Lphi_Ma_O0[2,1]", matrix = TRUE),
             prior_samps = post_subset(post, "rho_Lphi_Ma_O0_pr[2,1]", matrix = TRUE),
             xlim = xlim, y_max = y_max)
axis_labels("Parameter Value", "Probability")
```
